\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity

### 2014-07-07 paper.tex
fixed typos added probablistic bound

\vspace{10pt}
\noindent{\textbf{Grasp Quality Metrics}}: A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
We use the wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces.
We also consider the general case where there is friction at the contact points.
We follow the analysis of Schulman et al. \cite{schulman2011} in the discussion below.\\

@@

\section{Problem Definition}
Given a grasp $G$ on an object, we can define it by the following tuple $G = \lbrace c_1,...,c_m,n_1,...,n_m,z,\mu\rbrace$. We have a set $I$ of $m$ contacts on the object where $i \in I$ contact is located at $c_i$ with surface normal $n_i$.
The object has a center of mass $z$ and friction coefficient $\mu$.
We demonstrate that one can efficiently compute a closed form distribution for $c_i$,$n_i$ and $z$.
We note though that our metric assumes a given $\mu$. \\
% TODO: finish that thought

 For the following derivations we use the following notation.
 $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, hence $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS.
We further assume that the contacts on the gripper approach along a line of action: $x = \gamma(t): R \rightarrow R^d$.
% TODO: Michael, I changed this from voxel grid because we're modeling a continuous space not a voxel grid, the voxel grid willbe an artifact of our integration/sampling strategies.
We assume a bounded rectangular workspace $\mathcal{R}$.
The line segment has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig.
 \ref{fig:line_of_action}.
 % TODO: Draw a box around the workspace to show that b intersects the end of the workspace and draw a gripper approaching from a.  Also make A and B lowercase in the figure.
 We also define the function $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ as $f(x) = \mu(x)$ and an implicit surface $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
% TODO: Michael, did I fill this in correctly? It was left blank initially.

@@

\begin{equation}
P(c_{i,det} =  P(f(\gamma(g))=0|\theta(\gamma(t)))
\end{equation}

@@

\begin{equation}
p(c_i = \gamma(g), n_i = k) = p(n_i = k | h(\gamma(g)))*p(c_i = \gamma(g))
\end{equation}

@@

\begin{equation}
P(n_i = k) = \int_T  p(n_i = k | h(\gamma(g)))*p(c_i = \gamma(g)) dg
\end{equation}

@@

\begin{equation}
P(n_i = k) = \sum_T  p(n_i = k | h(\gamma(g)))*p(c_i = \gamma(g)) dg
\end{equation}

@@

\subsection{Other Thoughts (Not Finished)}
The derivation above assumes that the robot doesn't have any noise in its movements.
To accommodate noise in the position of the gripper at time $t$, $x_t$ given control input $u_{t}$ and previous states $x_{1:t-1}$, we introduce the following probability $P(x_t=k|u_t,x_{1:t-1})$.
This can be computed by methods like an Extended Kalman Filter (EKF) or a particle filter.
For simplicity we assume that it is a Gaussian distribution.

We know derive the following:

\begin{equation}
P(c_{i}) = \int P(c_{i,det}=\gamma(g),x_t = \gamma(g)) dg
\end{equation}

\section{Probabilistic Bound on Grasp Metric}

Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we prove that an extension is possible to give a probabilistic bound on the change in grasp quality.
We rewrite the results here:

@@

\begin{align}
\mbox{sup}_{x \in C(n)} <x,w> = <n,w> + \mu||n \times w||
\end{align}

@@

\begin{align}
h_{W_i(g)}(a,b) = <n_i,a+b\times(c_i-z)>+\mu ||n_i \times (a+b\times(c_i-z))||
\end{align}

@@

\subsection{Our Extension}
Setting $l_{i,a,b} = h_{W_i(g)}(a,b)$, we have for $||(a,b)|| \leq 1$ that is $|l_{i,a,b}(g) - l_{i,a,b}(g')|$ is bounded by $|<n_i,a+b\times (c_i-z)> - <n_i',a+b\times(c_i'-z')>|+\mu|||n_i \times (a+b \times (c_i -z)|| - ||n_i \times (a + b \times (c_i' - z')) |||$, using Theorem \ref{lemma35}. By using the following simple facts $||a|| \leq 1$, $||b|| \leq 1$,

>>>>

\vspace{10pt}
\noindent{\textbf{Grasp Quality Metrics}}: A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.
We use the wrench-space Ferrari-Canny force closure quality measures \cite{ferrari1992}, which aims to maximize the disturbance that can be resisted given bounds on the contact forces.
We also consider the general case where there is friction at the contact points.\\

@@

\section{Problem Definition}
Given a grasp $G$ on an object, we can define it by the following tuple $G = \lbrace c_1,...,c_m,n_1,...,n_m,z,\tau\rbrace$. We have a set $I$ of $m$ contacts on the object where $i \in I$ contact is located at $c_i$ with surface normal $n_i$.
The object has a center of mass $z$ and friction coefficient $\mu$.
We demonstrate that one can efficiently compute a closed form distribution for $c_i$,$n_i$ and $z$.
We note though that our metric assumes a known $\mu$ or friction coefficient. \\

 For the following derivations we use the following notation.
 $\theta(x) = \lbrace \mu(x),\Sigma(x) \rbrace$, hence $\theta(x)$ is a tuple consisting of the mean and covariance functions given by the trained GPIS.
We further assume that the contacts on the gripper approach along a line of action: $x = \gamma(t): R \rightarrow R^d$. The set of all elements in the range $[a,b]$ will be denoted by T. 
% TODO: Michael, I changed this from voxel grid because we're modeling a continuous space not a voxel grid, the voxel grid willbe an artifact of our integration/sampling strategies.
We assume a bounded rectangular workspace $\mathcal{R}$.
The line segment has endpoints $a,b$ that are defined as the start of the gripper and the intersection of the line with the end of the workspace respectively, as shown in Fig.
 \ref{fig:line_of_action}.
 % TODO: Draw a box around the workspace to show that b intersects the end of the workspace and draw a gripper approaching from a.  Also make A and B lowercase in the figure.
 We also define the function $f(x): \mathbb{R}^d \rightarrow \mathbb{R}$ as $f(x) = \mu(x)$ and an implicit surface $\mathcal{S} = \{ x \ | \ f(x) = 0 \}$.
% TODO: Michael, did I fill this in correctly? It was left blank initially.

@@

\begin{equation}
P(c_{i}) =  P(f(\gamma(t))=0|\theta(\gamma(t)))
\end{equation}

@@

\begin{equation}
p(c_i = \gamma(g), n_i = k) = p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t))
\end{equation}

@@

\begin{equation}
P(n_i = k) = \int_T  p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t)) dg
\end{equation}

@@

\begin{equation}
P(n_i = k) = \sum_T  p(n_i = k | h(\gamma(t)))*p(c_i = \gamma(t)) dg
\end{equation}

@@

\section{Probabilistic Bound on Grasp Metric}
Following recent work on proving a Lipschitz bound on the Ferrari-Canny Metric \cite{pokorny2013classical}, we prove that an extension is possible to give a probabilistic bound on the change in grasp quality.
We rewrite the results here:

@@

\begin{align}
\mbox{sup}_{x \in C(n)} <x,w> = <n,w> + \tau||n \times w||
\end{align}

@@

\begin{align}
h_{W_i(g)}(a,b) = <n_i,a+b\times(c_i-z)>+\tau ||n_i \times (a+b\times(c_i-z))||
\end{align}

@@

\subsection{Our Extension}
Setting $l_{i,a,b} = h_{W_i(g)}(a,b)$, we have for $||(a,b)|| \leq 1$ that is $|l_{i,a,b}(g) - l_{i,a,b}(g')|$ is bounded by $|<n_i,a+b\times (c_i-z)> - <n_i',a+b\times(c_i'-z')>|+\mu|||n_i \times (a+b \times (c_i -z)|| - ||n_i \times (a + b \times (c_i' - z')) |||$, using Theorem \ref{lemma35}. By using the following facts $||a|| \leq 1$, $||b|| \leq 1$, $||v \times w || \leq ||w||||v||$, $|<v,w>| \leq ||v||||w||$, we obtain:

\begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||n_i - n_i'||(1+||c_i - z||) \\
					&+ ||c_i - z_i - c_i'-z_i'|| \\
					&+ \mu(||n_i - n_i'||(1+||c_i - z||)\\
					&+||c_i - z_i-c_i'-z'||
\end{align*}

We now define the concept of a probabilistic bound by functions $\sigma(p)_{n_i}$ and $\sigma(p)_{r_i}$, given a probability $p$ they denote the change in grasp parameter from the mean in the distribution. $\sigma(p)_{n_i}$ references the distribution defined by $p(n_i = k)$. $r = c_i - \bar{z}$ defines a moment arm, where $\bar{z}$ is the expected center of mass, then $\sigma(p)_{r_i}$ references the distribution $p(c_i = k)$. We now write the bound as follows:

 \begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||\sigma_{n_i}(p)||(1+\bar{r}|) + ||\sigma_{r_i}(p)|| \\
                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
\end{align*}

For convenience we rewrite the bound on a given set of graps parameters as :

 \begin{align*}
b_i(p) &= ||\sigma_{n_i}(p)||(1+\bar{r}|) + ||\sigma_{r_i}(p)|| \\
                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
\end{align*}

To provide an upper bound overall contact parameters we introduce the following:

\begin{align}
b(p)  = \max_{i} b_i(p)
\end{align}

To prove if  this bound is preserved on

 \begin{align}
 q(g) = \min{(a,b) \in \mathbb{R}^6, ||u||=1} \max{i=1,..,m} l_{i,a,b}(g)
 \end{align}

we turn to the general case. $\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(p)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(p)$ and $\lambda(x)$ is bounded. Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$. We can ensure that is true.
